\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    {\Huge \scshape Pavan Sainath Reddy Vajrala} \\[5pt]
    \small \raisebox{-0.1\height}\faPhone\ \underline{+1 614-332-1793} ~
    \href{mailto:vajralapavansainathreddy@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{vajralapavansainathreddy@gmail.com}} ~
    \href{https://www.linkedin.com/in/pavan-sainath-reddy-}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/pavan-sainath-reddy-}}
\end{center}

% Profile Summary Section
\section{Profile Summary}\vspace{2mm}
\resumeSubHeadingListStart
    \item
    {
        Driven and technically proficient Master’s student in Computer Science with a strong foundation in Artificial Intelligence, Machine Learning, and Data Analysis. Leveraging a Bachelor's degree in Computer Science and Engineering, I possess hands-on experience in machine learning and natural language processing (NLP) through academic and internship projects. Skilled in programming and analytical problem-solving, I am enthusiastic about contributing to data-driven and AI-focused projects that drive innovation and deliver meaningful insights. Currently seeking opportunities to expand my expertise and make impactful contributions within a dynamic tech environment.
    }
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
 \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois}{2024 – Present}
      {\textit{Master's in Computer Science, CGPA: 3.7/4.0}}{Illinois, United States}
    \resumeSubheading
      {Kalasalingam Academy of Research and Education}{2020 – 2024}
      {\textit{B.Tech in Computer Science (AI \& ML), CGPA: 8.8/10.00}}{Tamil Nadu, India}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
      {Native Sparrow Software Solutions}{April 2023 – June 2023}
      {Machine Learning Intern}{Chennai, Tamil Nadu}
      \resumeItemListStart
        \item Developed and implemented machine learning models for real-time video data processing, gaining experience in creating practical, domain-specific use cases.
        \item Engineered a Python-based machine learning algorithm for traffic data analysis, resulting in a 30\% reduction in processing time and enabling academic users to make faster, data-driven decisions.
        \item Focused on enhancing software reliability and performance, creating robust training materials for academic tools.
      \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Job Simulations}
\resumeSubHeadingListStart
    \resumeSubheading
      {New York Jobs CEO Council}{November 2024}
      {Software Engineering Intern}{Virtual}
      \resumeItemListStart
        \item Completed a challenging simulation focused on debugging and developing features for the software engineering team.
        \item Resolved a critical bug in an automated billing system by skillfully identifying the root cause and developing an effective solution.
        \item Improved user experience by developing a code that supports a note-taking feature on each invoice, enhancing communication and transparency between senders and recipients.
      \resumeItemListEnd

    \resumeSubheading
      {British Airways Data Science Job Simulation on Forage}{February 2025}
      {Data Science Intern}{Virtual}
      \resumeItemListStart
        \item Completed a simulation focusing on how data science is a critical component of British Airways' success.
        \item Scraped and analyzed customer review data to uncover findings.
        \item Built a predictive model to understand factors that influence buying behavior.
      \resumeItemListEnd

    \resumeSubheading
      {AWS APAC Solutions Architecture Virtual Experience Program on Forage}{November 2024}
      {Solutions Architecture Intern}{Virtual}
      \resumeItemListStart
        \item Designed a simple and scalable hosting architecture based on Elastic Beanstalk for a client experiencing significant growth and slow response times.
        \item Described the proposed architecture in plain language, ensuring the client understood how it works and how costs will be calculated.
      \resumeItemListEnd
\vspace{-2pt}
    \resumeSubheading
      {Walmart USA Advanced Software Engineering Virtual Experience Program on Forage}{February 2025}
      {Advanced Software Engineering Intern}{Virtual}
      \resumeItemListStart
        \item Completed the Advanced Software Engineering Job Simulation where I solved difficult technical projects for a variety of teams at Walmart.
        \item Developed a novel version of a heap data structure in Java for Walmart’s shipping department, showcasing strong problem-solving and algorithmic skills.
        \item Designed a UML class diagram for a data processor, considering different operating modes and database connections.
        \item Created an entity relationship diagram to design a new database accounting for all requirements provided by Walmart’s pet department.
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

\textbf{Automated Diabetic Retinopathy Prediction} $|$ \emph{Python, TensorFlow, Keras} \hfill \textit{August 2023}
\begin{itemize}
    \item Implemented a deep learning-based Modified DenseNet model to detect diabetic retinopathy from retinal images, achieving high accuracy and sensitivity.
    \item Preprocessed large datasets using image augmentation techniques to enhance model robustness and improve prediction performance.
    \item Optimized the DenseNet architecture by fine-tuning hyperparameters and integrating dropout layers to prevent overfitting, improving overall model precision.
\end{itemize}

\textbf{Cryptowatch} $|$ \emph{Python, TensorFlow, scikit-learn, SQL} \hfill \textit{January 2024}
\begin{itemize}
    \item Developed a machine learning-based system to monitor cryptocurrency price fluctuations and predict future trends using real-time market data.
    \item Implemented supervised learning models such as Random Forest and LSTM to analyze historical data and forecast cryptocurrency prices with a prediction accuracy of 85\%.
    \item Integrated APIs for real-time data fetching, automated pipeline execution, and dynamic visualization of market trends, enabling user-friendly insights into trading opportunities.
\end{itemize}

\textbf{COVID-19 Dashboard} $|$ \emph{Tableau, Python, MS Excel, SQL} \hfill \textit{March 2022}
\begin{itemize}
    \item Created an interactive COVID-19 dashboard to visualize global and country-specific statistics, including confirmed cases, recoveries, and fatalities, using real-time data from reliable sources.
    \item Designed targeted filters for user-selected metrics in the COVID-19 dashboard; enhanced overall engagement by 30\% through improved navigation and access to critical information relevant during rapidly changing circumstances.
    \item Collaborated with a cross-functional team to ensure the dashboard met user requirements, resulting in a comprehensive and intuitive interface for health professionals and policymakers.
\end{itemize}

\textbf{Traffic Sign Recognition System} $|$ \emph{Python, TensorFlow, OpenCV} \hfill \textit{October 2024}
\begin{itemize}
    \item Developed a machine learning-based system to recognize and classify traffic signs using image data from the German Traffic Sign Recognition Benchmark (GTSRB).
    \item Implemented a Convolutional Neural Network (CNN) for feature extraction and classification, achieving an accuracy of 96\% on the test dataset.
    \item Preprocessed image data using techniques such as resizing, normalization, and augmentation to improve model generalization and robustness.
    \item Integrated the system into a prototype application for real-time traffic sign detection and classification, simulating autonomous vehicle scenarios.
\end{itemize}

%-----------TECHNICAL SKILLS-----------
\section*{Technical Skills}
\begin{itemize}
    \setlength{\itemsep}{0pt} % Reduces the space between items
    \item \textbf{Programming Languages:} Java, Python, C++, R.
    \item \textbf{Databases:} SQL, MongoDB, PostgreSQL.
    \item \textbf{Frameworks and Libraries:} Pandas, NumPy, TensorFlow, PyTorch.
    \item \textbf{Visualization Tools:} Tableau, Power BI, Matplotlib.
    \item \textbf{Tools and IDEs:} Git, GitHub, Visual Studio Code, PyCharm, Jupyter Notebook, Docker.
    \item \textbf{Operating Systems:} Unix, Windows, Linux.
    \item \textbf{Soft Skills:} Time Management, Problem Solving, Teamwork, Creativity, Work Ethic, Adaptability.
    \item \textbf{Areas of Interest:} Artificial Intelligence, Machine Learning, Data Analytics.
\end{itemize}

\section*{Certifications}
\item \textbf{\href{https://skillshop.credential.net/9c8571fe-ad59-4984-b8b5-6c0470d70f73}{Google Analytics Certification}} \hfill \textit{2024}
\begin{itemize}
\item Gained proficiency in analyzing website traffic, user behavior, and key performance metrics using Google Analytics tools.
\item Developed expertise in setting up tracking, interpreting reports, and leveraging data-driven insights to optimize marketing strategies.
\end{itemize}
\item \textbf{\href{https://www.coursera.org/account/accomplishments/professional-cert/3P5H4ZJ6XQXA}{IBM Machine Learning Professional}} \hfill \textit{2023}
\begin{itemize}
\item Acquired hands-on skills in building, training, and deploying machine learning models using Python libraries (Scikit-Learn, Pandas) and IBM Cloud services for real-world applications.
\item Developed expertise in core machine learning concepts, including supervised/unsupervised learning, model evaluation, and data preprocessing techniques.
\end{itemize}
\item \textbf{\href{https://www.credly.com/badges/c5e2a324-14f0-4893-9e3a-ccb7c7e3ce4b/public_url}{IBM Machine Learning Graduate}} \hfill \textit{2024}
\begin{itemize}
\item Learned how to build and improve machine learning models to solve real-world problems, focusing on both classification and clustering techniques.
\item Practiced using Python tools (like Scikit-Learn and Pandas) and IBM Cloud to create and deploy machine learning projects.
\end{itemize}

\section{Extracurricular Activities}
\resumeSubheading
    {UIS International Festival Volunteer}{October 2024 – November 2024}
    {University of Illinois Springfield} {Arts and Culture}
    \resumeItemListStart
        \resumeItem{Volunteered as a front desk check-in member, assisting with guest registration and providing event information.}
        \resumeItem{Helped coordinate festival activities, ensuring a welcoming experience for attendees.}
    \resumeItemListEnd

\section*{Publications}
\textbf{\href{https://ieeexplore.ieee.org/document/10425652}{Automated Diabetic Retinopathy Prediction using a Deep Learning-based Modified DenseNet}} \\
\emph{2023 2nd International Conference on Futuristic Technologies (INCOFT)} \hfill December 2023
\begin{itemize}
    \item Presented a deep learning approach for predicting diabetic retinopathy using a modified DenseNet architecture, improving accuracy and efficiency in diagnosis.
    \item Optimized model performance by leveraging data augmentation techniques and fine-tuning the DenseNet architecture, achieving significant improvements in sensitivity and specificity.
    \item Developed an end-to-end solution that integrated preprocessing, model training, and evaluation, providing a comprehensive tool for automated retinopathy detection in clinical environments.
\end{itemize}


\end{document}
